---
title: "SQL exercise - Task 4"
description: |
  Load data from PostgreSQL and create impressive plots.
author:
  - name: Niklas Moser, Tsun Fung Yau, Tze-Li Liu
date: "`r Sys.Date()`"
output:  
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  html_notebook:
    number_sections: yes
    toc: yes
    toc_float: yes
  radix::radix_article:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install packages if missing
if (!("RPostgreSQL" %in% installed.packages())){
  install.packages("RPostgreSQL")
}
if (!("getPass" %in% installed.packages())){
  install.packages("getPass")
}

# load packages
require(RPostgreSQL)
require(getPass)

# establish the connection
drv <- dbDriver('PostgreSQL')
con <- dbConnect(drv, host='v45522.1blu.de', port=5432, user=getPass('Provide the user'), 
                 password=getPass('Provide the password'), dbname='datamanagement')
```

## Solution

```{sql connection=con, output.var="data"}
select 
  h.hobo_id,
  st_x(h.geom) as x,
  st_y(h.geom) as y,
  avg(rd.temperature) as "mean"
from raw_data rd
join hobos h on h.id=rd.hobo_id
where h.year=2020
group by h.hobo_id, x, y
```

```{r}
library(cowplot)
library(tidyverse)

p1 <- ggplot(data, aes(x=y, y=mean)) + 
  xlim(47.95,48.071061)+
  geom_point()+
  theme_minimal()+
  xlab("Latitude in °N")+
  ylab("Mean Temperature [°C]")+
  theme(panel.border = element_rect(colour = "black", fill=NA))


p2 <- ggplot(data, aes(x=x, y=mean)) + 
  xlim(7.76,7.930848)+
  geom_point()+
  theme_minimal()+
  xlab("Longitude in °E")+
  ylab("Mean Temperature [°C]")+
  theme(panel.border = element_rect(colour = "black", fill=NA))

plot_grid(p1,p2, align = "h")

```


```{r}
require(ggplot2)
library(sf)
library(ggplot2)
library(dplyr)
library(readr)

#shapefile <- read_sf(dsn = "https://github.com/data-hydenv/data/blob/master/GIS/freiburg_districts_shp" , layer = "stadtteile")



ggplot(data = data)  +
  geom_point(aes(x=x, y=y,color=mean), size =2) +
  xlim(7.76,7.930848) +
  ylim(47.95,48.071061) +
  xlab("Longitude")+
  ylab("Latitude")+
    scale_color_gradient2(aes(colour="Average Temperature [°C]"), low="blue",high = "red", midpoint = median(data$mean))+
  theme_minimal()+
  theme(panel.background = element_rect(fill="grey50"))+
  theme(panel.border = element_rect(colour = "black", fill=NA))
             
```


```{r}
library(readr) ; library(dplyr) ; library(tidyr) ; library(rgdal)

#
pointHOBO <- SpatialPoints(coords = data.frame(x = data$x , y = data$y) , proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ")) %>% 
  spTransform("+proj=tmerc +lat_0=0 +lon_0=9 +k=1 +x_0=3500000 +y_0=0 +ellps=bessel +towgs84=598.1,73.7,418.2,0.202,0.045,-2.455,6.7 +units=m +no_defs") %>% 
  SpatialPointsDataFrame(data = data)

#
library(spdep) ; library(GISTools)

DistMtrx <- gDistance(pointHOBO , byid = TRUE)
DistNb <- mat2listw(DistMtrx , style = "W")

Nb <- DistNb

moran.test(pointHOBO$mean , Nb)
```

To test whether the variable (here as the mean temperature) is independent of location or not in a quantified way, a common-used method is the **Moran's I test**. If the temperature is independent of location, the spatial distribution of the temperature should be random. On the other hand, if there is correlation between temperature and location, points with similar values of temperature should locate close to each other. The Moran's I statistic aims to compare the similarity of each points with the nearby points on the temperature value. The coefficients of correlation of temperature values between all the points were calculated, and then weighted by the distance between points (closer distance, higher weight). The result of the Moran's I test is shown above. There is no significance in spatial dependency in this case. 


```{r}
dbDisconnect(con)
```

