---
title: "SQL exercise - Task 2"
description: |
  Create basic metadata about your Hobo.
author:
  - name: Mirko Mälicke
    url: https://hyd.iwg.kit.edu/personen_maelicke.php
    affiliation: Karlsruhe Institute for Technology (KIT)
    affiliation_url: https://hyd.iwg.kit.edu
date: "`r Sys.Date()`"
output:  
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  html_notebook:
    number_sections: yes
    toc: yes
    toc_float: yes
  radix::radix_article:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install packages if missing
if (!("RPostgreSQL" %in% installed.packages())){
  install.packages("RPostgreSQL")
}
if (!("getPass" %in% installed.packages())){
  install.packages("getPass")
}
if (!("leaflet" %in% installed.packages())){
  install.packages("leaflet")
}
if (!("wellknown" %in% installed.packages())){
  install.packages("wellknown")
}

# load packages
require(RPostgreSQL)
require(getPass)

# establish the connection
drv <- dbDriver('PostgreSQL')
con <- dbConnect(drv, host='v45522.1blu.de', port=5432, user=getPass('Provide the user'), 
                 password=getPass('Provide the password'), dbname='datamanagement')
```

## Solution

This task is considered to be finished when the chunk below is producing the output requested in the task description. Change this section and add the neccessary code to produce the output.

```{sql connection=con}
SELECT * FROM overview
```

## hobos within 2km radius query

```{sql connection=con}
SELECT hobo_id,
  st_astext(st_buffer(st_transform(geom, 25832), 2000)) as "hobos_within_2km"
FROM hobos

```

## hobos within 2km radius query in 2019

```{sql connection=con}
SELECT hobo_id,
  st_astext(st_buffer(st_transform(geom, 25832), 2000)) as "hobos_within_2km",
  year
FROM hobos WHERE year = 2019

```


## Hints

The follwoing chunks might help you to get started.

If you are dealing with PostGIS, it's often easier to select the HOBOs with human readable locations, as well.
This can be done like:
```{sql connection=con}
SELECT 
  id, 
  hobo_id,
  st_asewkt(geom) as "WKT",
  geom 
FROM hobos

```

Then, you can chain different spatial operations to implement a GIS workflow. To get the distance to a specific point we need to
transform the coordinates and then calculate the distance to that point. First the transform:
```{sql connection=con}
SELECT 
  id, 
  hobo_id,
  st_asewkt(st_transform(geom, 25832)) as "WKT",
  st_transform(geom, 25832) as "geom"
FROM hobos
```

A distance can be calculated like:
```{sql connection=con}
select st_distance(st_geomfromtext('POINT (0 0)'), st_geomfromtext('POINT (1 1)'))
```

You can calculate a 1km buffer around a hobo like:
```{sql connection=con}
SELECT 
  hobo_id,
  st_astext(st_buffer(st_transform(geom, 25832), 1000)) as "Buffer"
FROM hobos
```

We can also transform that back to the reference system used in leaflet and export as WKT. To do so, you need to group all
HOBOs into a single GeometryCollection or MultiPolygon.
```{sql connection=con, output.var="hobos"}
SELECT 
  st_astext(geom) as "Buffered" FROM 
(SELECT 
 1 as op, st_collect(st_transform(st_buffer(st_transform(geom, 25832), 1000), 4326)) as geom
FROM hobos group by op) t

```

```{r}
library(wellknown)

wktview(hobos$Buffered, center=c(7.8, 48), zoom=11)
```

