---
title: "SQL exercise - Task 2"
description: |
  Create basic metadata about your Hobo.
author:
  - name: Mirko Mälicke
    url: https://hyd.iwg.kit.edu/personen_maelicke.php
    affiliation: Karlsruhe Institute for Technology (KIT)
    affiliation_url: https://hyd.iwg.kit.edu
date: "`r Sys.Date()`"
output:  
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  html_notebook:
    number_sections: yes
    toc: yes
    toc_float: yes
  radix::radix_article:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install packages if missing
if (!("RPostgreSQL" %in% installed.packages())){
  install.packages("RPostgreSQL")
}
if (!("getPass" %in% installed.packages())){
  install.packages("getPass")
}
if (!("leaflet" %in% installed.packages())){
  install.packages("leaflet")
}
if (!("wellknown" %in% installed.packages())){
  install.packages("wellknown")
}

# load packages
require(RPostgreSQL)
require(getPass)

# establish the connection
drv <- dbDriver('PostgreSQL')
con <- dbConnect(drv, host='v45522.1blu.de', port=5432, user=getPass('Provide the user'), 
                 password=getPass('Provide the password'), dbname='datamanagement')
```

## Solution

This task is considered to be finished when the chunk below is producing the output requested in the task description. Change this section and add the neccessary code to produce the output.

```{sql connection=con}
SELECT * FROM overview
```


## See tables in db

```{r}
dbListTables(con)
```


## count nr of raw data:

```{sql connection=con}
SELECT t2.hobo_id, count(*) AS raw_data
FROM 
  raw_data t1
LEFT JOIN 
  (SELECT id, hobo_id FROM hobo) t2
ON  t1.hobo_id = t2.id
GROUP BY t2.hobo_id 
```


## count nr of quality checked data:
```{sql connection=con}
SELECT hobo_id, count(*) AS checked_data FROM quality_checked GROUP BY hobo_id ORDER BY hobo_id ASC
```


## hobos within 2km radius query in 2020
```{sql connection=con}
SELECT a.hobo_id, count(b.hobo_id) AS within_2020
FROM 
    (SELECT hobo_id, st_union(geom) AS geom FROM hobo GROUP BY hobo_id) a,
    (SELECT hobo_id, st_union(geom) AS geom, year FROM hobo GROUP BY hobo_id, year) b 
WHERE st_dwithin(st_transform(a.geom, 25832), st_transform(b.geom, 25832), 2000) AND a.hobo_id != b.hobo_id AND b.year = 2020
GROUP BY a.hobo_id 
ORDER BY hobo_id DESC
```


## hobos within 2km radius query

```{sql connection=con}
SELECT a.hobo_id, count(b.hobo_id) AS within
FROM 
    (SELECT hobo_id, st_union(geom) AS geom FROM hobo GROUP BY hobo_id) a,
    (SELECT hobo_id, st_union(geom) AS geom, year FROM hobo GROUP BY hobo_id, year) b 
WHERE st_dwithin(st_transform(a.geom, 25832), st_transform(b.geom, 25832), 2000) AND a.hobo_id != b.hobo_id
GROUP BY a.hobo_id 
ORDER BY hobo_id DESC
```


## used in year

```{sql connection=con}
SELECT hobo_id, year = 2020 AS used_in_2020,  year = 2018 AS used_in_2018, year = 2017 AS used_in_2017 FROM hobos
```


## join queries and create view
```{sql connection = con}
CREATE VIEW overview AS
SELECT raw.hobo_id, raw.raw_data, checked.checked_data, w_2020.within_2020 AS within_2k_2020, w.within AS within_2k,
u.used_in_2020, u.used_in_2018, u.used_in_2017
FROM 
  (SELECT t2.hobo_id, count(*) AS raw_data FROM raw_data t1
   LEFT JOIN 
    (SELECT id, hobo_id FROM hobo) t2
   ON  t1.hobo_id = t2.id
   GROUP BY t2.hobo_id) raw

LEFT JOIN
  (SELECT hobo_id, count(*) AS checked_data FROM quality_checked GROUP BY hobo_id) checked
ON raw.hobo_id = checked.hobo_id

LEFT JOIN
  (SELECT a.hobo_id, count(b.hobo_id) AS within_2020
   FROM 
    (SELECT hobo_id, st_union(geom) AS geom FROM hobo GROUP BY hobo_id) a,
    (SELECT hobo_id, st_union(geom) AS geom, year FROM hobo GROUP BY hobo_id, year) b 
   WHERE st_dwithin(st_transform(a.geom, 25832), st_transform(b.geom, 25832), 2000)
   AND a.hobo_id != b.hobo_id AND b.year = 2020
   GROUP BY a.hobo_id) w_2020
ON raw.hobo_id = w_2020.hobo_id

LEFT JOIN
  (SELECT a.hobo_id, count(b.hobo_id) AS within
   FROM 
    (SELECT hobo_id, st_union(geom) AS geom FROM hobo GROUP BY hobo_id) a,
    (SELECT hobo_id, st_union(geom) AS geom, year FROM hobo GROUP BY hobo_id, year) b 
   WHERE st_dwithin(st_transform(a.geom, 25832), st_transform(b.geom, 25832), 2000) AND a.hobo_id != b.hobo_id
   GROUP BY a.hobo_id) w
ON raw.hobo_id = w.hobo_id

LEFT JOIN
  (SELECT hobo_id, year = 2020 AS used_in_2020,  year = 2018 AS used_in_2018, year = 2017 AS used_in_2017 FROM hobos) u
ON raw.hobo_id = u.hobo_id

```   
   
   
## some helper queries to figure out stuff:

```{sql connection = con}

SELECT hobo_id, st_asewkt(st_union(geom)) AS geom, year FROM hobo GROUP BY hobo_id, year ORDER BY hobo_id ASC


```


```{sql connection = con}

SELECT a.hobo_id, b.hobo_id AS b_id, st_asewkt(b.geom) AS geom
FROM 
    (SELECT hobo_id, st_union(geom) AS geom FROM hobo GROUP BY hobo_id) a,
    (SELECT hobo_id, geom AS geom FROM hobo) b 
WHERE st_dwithin(st_transform(a.geom, 25832), st_transform(b.geom, 25832), 2000) AND a.hobo_id = 10350083
ORDER BY b_id DESC

```


```{sql connection = con}

select *
from 
    hobos a, hobos b 
where st_dwithin(st_transform(a.geom, 25832), st_transform(b.geom, 25832), 2000) and a.hobo_id != b.hobo_id 

```

### union geometries of hobo devices
```{sql connection = con}
SELECT hobo_id, st_astext(st_union(geom)) AS geom FROM hobo GROUP BY hobo_id
```



## Hints

The follwoing chunks might help you to get started.

If you are dealing with PostGIS, it's often easier to select the HOBOs with human readable locations, as well.
This can be done like:
```{sql connection=con}
SELECT 
  id, 
  hobo_id,
  st_asewkt(geom) as "WKT",
  geom 
FROM hobos

```

Then, you can chain different spatial operations to implement a GIS workflow. To get the distance to a specific point we need to
transform the coordinates and then calculate the distance to that point. First the transform:
```{sql connection=con}
SELECT 
  id, 
  hobo_id,
  st_asewkt(st_transform(geom, 25832)) as "WKT",
  st_transform(geom, 25832) as "geom"
FROM hobos
```

A distance can be calculated like:
```{sql connection=con}
select st_distance(st_geomfromtext('POINT (0 0)'), st_geomfromtext('POINT (1 1)'))
```

You can calculate a 1km buffer around a hobo like:
```{sql connection=con}
SELECT 
  hobo_id,
  st_astext(st_buffer(st_transform(geom, 25832), 1000)) as "Buffer"
FROM hobos
```

We can also transform that back to the reference system used in leaflet and export as WKT. To do so, you need to group all
HOBOs into a single GeometryCollection or MultiPolygon.
```{sql connection=con, output.var="hobos"}
SELECT 
  st_astext(geom) as "Buffered" FROM 
(SELECT 
 1 as op, st_collect(st_transform(st_buffer(st_transform(geom, 25832), 1000), 4326)) as geom
FROM hobos group by op) t

```

```{r}
library(wellknown)

wktview(hobos$Buffered, center=c(7.8, 48), zoom=11)
```

